Viscous Erosion in Porous Media

### 2018-03-13 docs/methods/erosion_methods.tex
NM

We further quantify many of these observations in Fig.~\ref{fig:mbodyplots}. First, Fig.~\ref{fig:mbodyplots}(a) shows area fraction versus time. The area fraction is the total area of all bodies as compared to the domain area, i.e.~the 2D counterpart of volume fraction. The initial configuration of 6 circles comprises about 40\% of the domain area, and this percentage steadily decreases as the bodies erode. Figure \ref{fig:mbodyplots}(b) shows the inlet/outlet flow-rate, $\umax$, over time.

>>>>

We further quantify many of these observations in Fig.~\ref{fig:mbodyplots}. First, Fig.~\ref{fig:mbodyplots}(a) shows area fraction versus time. The area fraction is the total area of all bodies as compared to the domain area, i.e.~the 2D counterpart of volume fraction. The initial configuration of 6 circles comprises about 40\% of the domain area, and this percentage steadily decreases as the bodies erode. Figure \ref{fig:mbodyplots}(b) shows the inlet/outlet flow-rate, $\umax$, over time. Since we have fixed the pressure drop across the cell in these simulations, $\umax$ steadily increases as the bodies diminish and provide less resistance. Here, the vertical axis is logarithmic, and so the plot suggests exponential increase of $\umax$ at early times. This rapid increase in flow is likely due to the erosion-induced channelization observed above. In Fig.~\ref{fig:mbodyplots}(b) we show the total drag, summed over all bodies, versus time. Though the bodies diminish due to erosion, the steady increase of $\umax$ causes the total drag to remain relatively constant. Only near the end of the simulation does the drag decrease rapidly to zero.
